Concurrent Programming in Harmony

### 2020-10-09 book/paper.tex
Latest

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Anneke van Renesse,
Brendon Nguyen,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Anneke van Renesse,
Brendon Nguyen,
Heather Zheng,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
